Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2021-10-22 doc/AMS-15/AMS-15_poster.Rmd
Improve table titles

cons_df_sum %>% 
  arrange(fm_consensus) %>% 
  select(Name, `Consensus pMC` = fm_consensus,
         `Mean pMC` = fm_corr_mean,
         `Mean pMC error` = sig_fm_corr_mean,
         `Std. dev. of measurements` = fm_corr_sd,
         N) %>% 
gt() %>% 
  tab_header(title = "Summary statistics by sample type") %>% 
  fmt_number(2:5, 
             scale_by = 100,
             decimals = 2)
```

@@

```{r}
cons_df %>% 
  filter(Name %in% c("TIRI-I", "C-2", "NOSAMS2")) %>% 
  ungroup() %>% 
  summarize(across(c(sig_fm_corr, fm_diff),
                   list(mean = mean, sd = sd)),
            N = n()) %>% 
  select(`Consensus difference` = fm_diff_mean,
         `Std. Dev. of consensus difference` = fm_diff_sd,
         `per-sample error` = sig_fm_corr_mean,
         N
         ) %>%  
  gt() %>% 
  tab_header(title = "Summary statisics for reference materials",
             subtitle = "TIRI-I, C-2, and NOSAMS2. Values in pMC") %>% 
  fmt_number(1:3, 
             scale_by = 100,
             decimals = 2)
```

>>>>

cons_df_sum %>% 
  arrange(fm_consensus) %>% 
  select(Name, `Consensus pMC` = fm_consensus,
         `Mean pMC` = fm_corr_mean,
         `Mean pMC error` = sig_fm_corr_mean,
         `Std. dev. of measurements` = fm_corr_sd,
         N) %>% 
gt() %>% 
  tab_header(title = "Reference material precision and accuracy") %>% 
  fmt_number(2:5, 
             scale_by = 100,
             decimals = 2)
```

@@

```{r}
cons_df %>% 
  filter(Name %in% c("TIRI-I", "C-2", "NOSAMS2")) %>% 
  ungroup() %>% 
  summarize(across(c(sig_fm_corr, fm_diff),
                   list(mean = mean, sd = sd)),
            N = n()) %>% 
  select(`Consensus difference` = fm_diff_mean,
         `Std. Dev. of consensus difference` = fm_diff_sd,
         `per-sample error` = sig_fm_corr_mean,
         N
         ) %>%  
  gt() %>% 
  tab_header(title = "Reference material performance summary",
             subtitle = "TIRI-I, C-2, and NOSAMS2. Values in pMC") %>% 
  fmt_number(1:3, 
             scale_by = 100,
             decimals = 2)
```
